---
title: "Tidy Tuesday"
author: "Samuel W. Suk"
date: "4/10/2022"
output: html_document
---

#Story: Using a _ chart, I want to show what the main threat to bee colonies per state is over the past 6 years, and the percent that it impacts the number of colonies over all other stressors. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(ggplot2)
library(dplyr)
library(vtable)
library(tidyverse)
library(jtools)
library(fixest)
library(rdrobust)
library(margins)
```

## Importing Data
Website Link: https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-11/readme.md
```{r, echo=TRUE}

colony <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-11/colony.csv')
stressor <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-11/stressor.csv')

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Cleaning and Sorting the Data
```{r}
vtable(colony)
vtable(stressor)

# Colony Cleaning
colonystate <- subset(colony, select=c("state", "colony_n", "colony_lost", "colony_lost_pct"))


state_avg <- colonystate %>%
  filter(!is.na(colonystate)) %>%
  group_by(state) %>%
  summarise_at(c("colony_n", "colony_lost", "colony_lost_pct"), mean, na.rm = TRUE)


# Stressor Clean

stressor_clean <- stressor %>%
  filter(!is.na(stress_pct))

stressor_sum <- stressor_clean %>%
  group_by(state, stressor)%>%
  summarize(maxstress = max(stress_pct))

stressor_state <- stressor_sum %>%
  group_by(state) %>%
  top_n(1, maxstress)
```

##Joining the Dataframes
```{r}
combo_df <- full_join(state_avg, stressor_state, by = 'state', copy= TRUE)
```

##Visualizations
```{r}
visualization1 <- ggplot(data = combo_df, aes(x=maxstress, y= reorder(state, -maxstress), fill = stressor)) + geom_bar(stat = "identity", color = "black", fill = "yellow") + ggtitle("Largest Bee Stressor by State")
visualization1 + ylab("State") + xlab("Percent of Stress")

visualization2 <- ggplot(data = combo_df, aes(x=maxstress, y= reorder(state, -maxstress), fill = stressor)) + geom_bar(stat = "identity") + ggtitle("Largest Bee Stressor by State") + 
  scale_fill_manual(values=c("grey",
                             "Yellow"))
visualization2 + ylab("State") + xlab("Percent of Stress")
```
